---
title: "flexdashboard example"
subtitle: "https://martinctc.github.io"
author: "Martin Chan"
date: "2019"
output: 
  flexdashboard::flex_dashboard:
  orientation: columns
  vertical_layout: fill
---

<style>                     
.navbar {
  background-color: rgb(47,85,151);
}

</style>   


```{r setup, include=FALSE}
library(tidyverse)
library(ggiraph)
library(ggthemes)
library(flexdashboard)
library(dygraphs)
library(wordcloud2)
library(janeaustenr)
library(tidytext)

#' Make it pipe friendly
plot_ggiraph <- function(ggobject, ...){
  ggiraph::girafe(ggobj = ggobject, ...)
}

rgb2hex <- function(r,g,b) rgb(r, g, b, maxColorValue = 255)

```


Home {data-icon="fa-tachometer-alt"}
=====================================

Column {data-width=120}
-----------------------------------------------------------------------

### Introduction

> This is an example to showcase the visualisations we can create in a static HTML file, using the two R packages **flexdashboard** and **RMarkdown**.

In this dashboard, we use a number of canonical inbuilt datasets with R to display a variety of visualisations, including time-series charts, interactive scatter plots, word clouds, etc. 

Use the tabs in the navigation bar above to browse through the different visualisations.

### Average Sepal.Width of setosa [iris]
```{r}
iris %>%
  filter(Species == "setosa") %>%
  pull(Sepal.Width) %>%
  mean() %>%
  round(1) %>%
  valueBox(icon = "fa-spa")
```

### Average mpg of cars in [mpg] dataset
```{r}
mtcars %>% 
  pull(mpg) %>%
  mean() %>%
  round(1) %>%
  valueBox(color = rgb2hex(150,48,20), icon = "fa-car")
```

### Average height of beings on Tatooine [starwars]
```{r}
starwars %>%
  filter(homeworld == "Tatooine") %>%
  pull(height) %>%
  mean(na.rm = TRUE) %>%
  round(1) %>%
  valueBox(color = rgb2hex(112,48,160), icon = "fa-walking")
```


Column {data-width=250}
-----------------------------------------------------------------------

### Interactive Scatter Plot
```{r}
iris %>%
  mutate(tool_tip = paste0("Sepal Length: ", Sepal.Length,
                          "; Sepal Width: ", Sepal.Width,
                          "; Species: ", Species)) %>%
  ggplot(aes(x = Sepal.Length,
             y = Sepal.Width,
             colour = Species,
             data_id = Species,
             tooltip = tool_tip)) +
  geom_point_interactive() +
  ggtitle("Sepal Length and Sepal Width by iris Species",
          subtitle = "Dataset: iris") +
  ggthemes::theme_economist() -> gg

ggiraph::girafe(ggobj = gg, width = 7, height = 4)

```

### Time Series - Lung Deaths
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
  dySeries("mdeaths", label = "Male") %>%
  dySeries("fdeaths", label = "Female") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 20)
```

Column {data-width=250}
-----------------------------------------------------------------------

### Downloadable Interactive Table
```{r}
mtcars %>%
    DT::datatable(caption = "mtcars data table with download buttons",
                extensions = 'Buttons',
                options = list(bLengthChange = FALSE,
                               dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All"))))
```

### Word Cloud - Emma (Jane Austen)
```{r}
tibble(text = janeaustenr::emma) %>%
  tidytext::unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  wordcloud2() + WCtheme(1)

```

---


iris  {data-navmenu="Explore me" data-icon="fa-list"}
=====================================
Column {data-width=150}
-----------------------------------------------------------------------

### Overview 

Welcome to the dashboard! 

Use the above tabs to flick through different visualizations.

This current page is showing data from the *iris* dataset.

---

#### `iris` dataset

This is the famous iris dataset by Ronald Fisher.

Column {data-width=300 .tabset .tabset-fade}
-----------------------------------------------------------------------

### Interactive scatter plot
```{r}
iris %>%
  mutate(tool_tip = paste0("Sepal Length: ", Sepal.Length,
                          "; Sepal Width: ", Sepal.Width,
                          "; Species: ", Species)) %>%
  ggplot(aes(x = Sepal.Length,
             y = Sepal.Width,
             colour = Species,
             data_id = Species,
             tooltip = tool_tip)) +
  geom_point_interactive() +
  ggtitle("Sepal Length and Sepal Width by iris Species",
          subtitle = "Dataset: iris") +
  ggthemes::theme_economist()-> gg

ggiraph::girafe(ggobj = gg, width = 7, height = 4.5)

```

### Interactive scatterplot with facets

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iris %>%
  mutate(tool_tip = paste(Sepal.Length, Sepal.Width, sep = ", ")) %>%
  ggplot(aes(x = Sepal.Width, y = Sepal.Length, colour = Species,tooltip = tool_tip, data_id = tool_tip)) +
  geom_point_interactive() +
  facet_grid(cols = vars(Species)) +
  ggtitle("Example of a chart which will be a pain to build in Excel",
          subtitle = "(Especially if you want the interactivity as well)") +
  ggthemes::theme_igray()-> gg

ggiraph::girafe(ggobj = gg, width = 7, height = 3.5)
```

